cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_expbranches

>>>>

The `gen_expbranches(n, p, k)` function generates a dataset of $n$ points forming $k$ exponential branches in 2D, with optional noise dimensions to embed the structure in a \$p\$-dimensional space. These branches grow in opposite directions, producing a radiating curvilinear structure from a central region.

Each branch $i$ is constructed using:

$X\_1 \sim \mathcal{U}(-2, 2)$
$X\_2 = \exp(\pm s\_i \cdot X\_1) + \epsilon$,

where:
$\epsilon \sim \mathcal{U}(0, 0.1)$ adds local jitter
$s\_i \in \[0.5, 2]$ is randomly sampled for each branch.

The sign alternates between branches (odd: negative, even: positive exponent). This creates mirror-symmetric branches with different steepness and curvature where odd-numbered branches: decay pattern (reflected about $x$-axis) and even-numbered branches: growth pattern.

For $p > 2$, Gaussian noise is added to embed the $2\text{-}D$ branches in higher dimensions:

These represent irrelevant or noisy dimensions.
